---
title: "Analyse survey responses"
author: "Ana Martinovici"
date: "`r Sys.time()`"
output: 
    html_document:
        toc: true
        toc_float: 
            collapsed: false
        number_sections: true
        code_folding: hide
        theme: cerulean
editor_options: 
  chunk_output_type: console
---


```{r}

library("tidyverse")
library("Cairo")
library("here")

load(here::here("data", "survey_data.RData"))

```

# Number of responses

Of the `r nrow(processed_data)` observations in the dataset exported from Qualtrics, we exclude `r nrow(processed_data %>% filter(!is.na(excl_reason)))`:

```{r}

processed_data %>% 
	filter(!is.na(excl_reason)) %>% 
	group_by(excl_reason) %>% 
	summarise(n_obs = n())

analysis_sample <- processed_data %>% 
	filter(is.na(excl_reason)) %>%
	select(pseudo_ResponseID,
		 geographical_area,
		 years_experience,
		 area_study,
		 current_role,
		 software_analyze,
		 software_collect,
		 starts_with("years_"),
		 starts_with("excl_"),
		 starts_with("Please_Mark"),
		 starts_with("freq_"),
		 starts_with("DataTrans_"),
		 starts_with("ProcOrder_"),
		 likelihood_reproduce)

```

The analysis sample has `r nrow(analysis_sample)` responses.

# Years of experience

Answers to the question "How many years of experience do you have in this research area? Please list the number of years you have worked on studies in this area.":

- mean: `r round(mean(analysis_sample[["years_experience"]]), 1)`

- median: `r median(analysis_sample[["years_experience"]])`

```{r}

figure_number <- 2

My_Theme <- theme(
	text = element_text(size = 14),
	axis.title.x = element_text(size = 14),
	axis.title.y = element_text(size = 14)
)

analysis_sample %>%
	ggplot(aes(x = years_experience)) +
	geom_bar(color = "white", fill = "#56B4E9") +
	theme_bw() +
	labs(y = "Number of responses",
	     x = "Years of experience") + 
	My_Theme

ggsave(filename = here::here("figures", 
				     paste0("Fig", figure_number, 
				     	 "_years_experience.png")),
	 width = 8, height = 5, dpi = 500,
	 type = "cairo")

figure_number <- figure_number + 1

```


```{r}

df_years_experience <- analysis_sample %>%
	select(pseudo_ResponseID,
		 starts_with("years_")) %>%
	select(-years_experience) %>%
	pivot_longer(-pseudo_ResponseID,
			 names_to = "var_name",
			 values_to = "var_value") %>%
	mutate(var_name = factor(var_name,
					 levels = c("years_CollectRT",
					 	     "years_AnalyseRT",
					 	     "years_OS",
					 	     "years_ExperimentCoding",
					 	     "years_AnalysisCoding"),
					 labels = c("Collecting RT",
					 	     "Analyzing RT",
					 	     "Open Science",
					 	     "Experiment coding",
					 	     "Analysis coding")))

df_years_experience <- df_years_experience %>%
	mutate(var_value = factor(var_value,
					  levels = c(NA,
					  	     "< 1 year",
					  	     "1 - 3 years",
					  	     "4 - 6 years",
					  	     "7 - 9 years",
					  	     "10+ years"),
					  labels = c("n.a.",
					  	     "< 1 year",
					  	     "1 - 3 years",
					  	     "4 - 6 years",
					  	     "7 - 9 years",
					  	     "10+ years"),
					  exclude = NULL))


df_years_experience %>%
	ggplot(aes(x = var_value)) +
	# fill with blue color, white borders of the bars
	geom_bar(color = "white", fill = "#56B4E9") + 
	theme_bw() +
	facet_wrap(vars(var_name)) +
	scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
	#text on the x axis is black
	theme(axis.text.x = element_text(colour = "black")) + 
	# Change facet label  background colour
	theme(strip.background = element_rect(fill = "white")) + 
	# Change facet label text colour
	theme(strip.text = element_text(colour = "black")) + 
	labs(x = "",
	     y = "Number of responses") +
	My_Theme

ggsave(filename = here::here("figures", 
				     paste0("Fig", figure_number, 
				     	 "_years_involvement.png")),
	 width = 10, height = 7, dpi = 500,
	 type = "cairo")

figure_number <- figure_number + 1

```


# Data exclusions

Frequency of excluding, reporting, and reporting the exact number of participants (part), stimuli, and trials due to:

```{r}
aux_df <- analysis_sample %>%
	select(pseudo_ResponseID,
		 contains("_ExtEvent_"),
		 contains("_FixedCr_"),
		 contains("_DataDepCr_")) %>%
	select(-contains("feedback"),
		 -contains("importance"))
aux_df <- aux_df %>%
	pivot_longer(-pseudo_ResponseID,
			 names_to = "var_name",
			 values_to = "var_value")
aux_df <- aux_df %>%
	mutate(var_name = str_sub(var_name, start = 6)) %>%
	mutate(var_name = str_replace(var_name, "excl", "Exclude")) %>%
	mutate(var_name = str_replace(var_name, "rep_exact", "ReportExact")) %>%
	mutate(var_name = str_replace(var_name, "rep", "Report"))
aux_df <- aux_df %>%
	separate(var_name,
		   into = c("excl_due_to", "do_what", "level_of_data"),
		   sep = "_")
aux_df <- aux_df %>%
	mutate(var_value = factor(var_value,
					  levels = c(NA,
					  	     "Never",
					  	     "Sometimes",
					  	     "About half the time",
					  	     "Most of the time",
					  	     "Always"),
					  labels = c("n.a.",
					  	     "Never",
					  	     "Sometimes",
					  	     "About half the time",
					  	     "Most of the time",
					  	     "Always"),
					  exclude = NULL))

df_exclude <- aux_df %>%
	filter(do_what == "Exclude")

df_report <- df_exclude %>%
	filter(var_value %in% c("Sometimes",
					"About half the time",
					"Most of the time",
					"Always")) %>%
	select(pseudo_ResponseID,
		 excl_due_to,
		 level_of_data) %>%
	left_join(aux_df %>%
		    	filter(do_what %in% c("Report", "ReportExact")),
		    by = c("pseudo_ResponseID", "excl_due_to", "level_of_data"))

aux_df <- rbind(df_exclude,
		    df_report)

aux_df <- aux_df %>%
	mutate(level_of_data = factor(level_of_data,
						levels = c("part",
							     "stimuli",
							     "trials"),
						labels = c("Participants",
							     "Stimuli",
							     "Trials"))) %>%
	mutate(do_what = factor(do_what,
					levels = c("Exclude",
						     "Report",
						     "ReportExact"),
					labels = c("Exclude",
						     "Report excluding",
						     "Report the exact number\nof excluded observations")))

aux_df %>%
	filter(excl_due_to %in% c("ExtEvent")) %>%
	ggplot(aes(x = var_value)) +
	# fill with blue color, white borders of the bars
	geom_bar(color = "white",fill = "#56B4E9") + 
	theme_bw() +
	facet_grid(level_of_data ~ do_what) +
	theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
	# Change facet label background colour
	theme(strip.background = element_rect(fill = "white")) + 
	# Change facet label text colour
	theme(strip.text = element_text(colour = 'black')) + 
	labs(y = "Number of responses",
	     x = "") +
	My_Theme

ggsave(filename = here::here("figures", 
				     paste0("Fig", figure_number, 
				     	 "_frequency_externalevents.png")),
	 width = 10, height = 7, dpi = 500,
	 type = "cairo")

figure_number <- figure_number + 1

```


```{r}
aux_df %>%
	filter(excl_due_to %in% c("FixedCr")) %>%
	ggplot(aes(x = var_value)) +
	geom_bar(color = "white", fill = "#56B4E9") +
	theme_bw() +
	facet_grid(level_of_data ~ do_what) +
	theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
	theme(strip.background = element_rect(fill = "white")) + 
	theme(strip.text = element_text(colour = 'black')) + 
	labs(y = "Number of responses",
	     x = "") +
	My_Theme

ggsave(filename = here::here("figures", 
				     paste0("Fig", figure_number, 
				     	 "_frequency_fixedcriteria.png")),
	 width = 10, height = 7, dpi = 500,
	 type = "cairo")

figure_number <- figure_number + 1

```


```{r}
aux_df %>%
	filter(excl_due_to %in% c("DataDepCr")) %>%
	ggplot(aes(x = var_value)) +
	geom_bar(color = "white", fill = "#56B4E9") + 
	theme_bw() +
	facet_grid(level_of_data ~ do_what) +
	theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
	theme(strip.background = element_rect(fill = "white")) + 
	theme(strip.text = element_text(colour = 'black')) + 
	labs(y = "Number of responses",
	     x = "") +
	My_Theme

ggsave(filename = here::here("figures", 
				     paste0("Fig", figure_number, 
				     	 "_frequency_datadependent.png")),
	 width = 10, height = 7, dpi = 500,
	 type = "cairo")

figure_number <- figure_number + 1

```

Importance ("How important do you think this processing step is for accuracy in analyses and interpretation?")

```{r}

aux_df <- analysis_sample %>%
	select(pseudo_ResponseID,
		 contains("_ExtEvent_"),
		 contains("_FixedCr_"),
		 contains("_DataDepCr_")) %>%
	select(pseudo_ResponseID,
		 contains("importance"))
aux_df <- aux_df %>%
	pivot_longer(-pseudo_ResponseID,
			 names_to = "var_name",
			 values_to = "var_value")
aux_df <- aux_df %>%
	mutate(var_name = str_remove(var_name, "excl_")) %>%
	mutate(var_name = str_remove(var_name, "_importance"))
aux_df <- aux_df %>%
	mutate(var_name = factor(var_name,
					 levels = c("ExtEvent",
					 	     "FixedCr",
					 	     "DataDepCr"),
					 labels = c("Events beyond\nthe researcher's control",
					 	     "Fixed criteria",
					 	     "Data-dependent criteria")))
aux_df <- aux_df %>%
	mutate(var_value = factor(var_value,
					  levels = c(NA,
					  	     "Not at all important",
					  	     "Slightly important",
					  	     "Moderately important",
					  	     "Very important",
					  	     "Extremely important"),
					  labels = c("n.a.",
					  	     "Not at all",
					  	     "Slightly",
					  	     "Moderately",
					  	     "Very",
					  	     "Extremely"),
					  exclude = NULL))

aux_df %>%
	ggplot(aes(x = var_value)) +
	geom_bar(color = "white", fill = "#56B4E9") +
	theme_bw() +
	facet_wrap(vars(var_name)) +
	theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
	theme(strip.background = element_rect(fill = "white")) + 
	theme(strip.text = element_text(colour = "black")) +
	labs(y = "Number of responses",
	     x = "") +
	My_Theme

ggsave(filename = here::here("figures", 
				     paste0("Fig", figure_number, 
				     	 "_importance_C123.png")),
	 width = 10, height = 7, dpi = 500,
	 type = "cairo")

figure_number <- figure_number + 1

```

# Data processing and transformations

```{r}

aux_df <- analysis_sample %>%
	select(pseudo_ResponseID,
		 contains("DataTrans"),
		 contains("ProcOrder")) %>%
	select(-contains("importance"),
		 -contains("feedback"))
aux_df <- aux_df %>%
	pivot_longer(-pseudo_ResponseID,
			 names_to = "var_name",
			 values_to = "var_value")
aux_df <- aux_df %>%
	mutate(var_name = str_remove(var_name, "freq_"))
aux_df <- aux_df %>%
	mutate(var_value = factor(var_value,
					  levels = c(NA,
					  	     "Never",
					  	     "Sometimes",
					  	     "About half the time",
					  	     "Most of the time",
					  	     "Always"),
					  labels = c("n.a.",
					  	     "Never",
					  	     "Sometimes",
					  	     "About half the time",
					  	     "Most of the time",
					  	     "Always"),
					  exclude = NULL))

df_use <- aux_df %>%
	filter(var_name == "DataTrans_do")

df_report <- df_use %>%
	filter(var_value %in% c("Sometimes",
					"About half the time",
					"Most of the time",
					"Always")) %>%
	select(pseudo_ResponseID) %>%
	left_join(aux_df %>%
		    	filter(var_name == "DataTrans_report"),
		    by = c("pseudo_ResponseID"))

aux_df <- rbind(df_use,
		    df_report,
		    aux_df %>%
		    	filter(var_name == "ProcOrder_report"))

aux_df <- aux_df %>%
	mutate(var_name = factor(var_name,
					 levels = c("DataTrans_do",
					 	     "DataTrans_report",
					 	     "ProcOrder_report"),
					 labels = c("Use data transformations",
					 	     "Report data transformations",
					 	     "Report processing order")))

aux_df %>%
	ggplot(aes(x = var_value)) +
	geom_bar(color = "white", fill = "#56B4E9") + 
	theme_bw() +
	ylab("Number of responses") +
	xlab("") +
	facet_wrap(vars(var_name)) +
	theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
	theme(strip.background = element_rect(fill = "white")) + 
	theme(strip.text = element_text(colour = "black")) + 
	labs(y = "Number of responses",
	     x = "") +
	My_Theme

ggsave(filename = here::here("figures", 
				     paste0("Fig", figure_number, 
				     	 "_data_transformations.png")),
	 width = 10, height = 7, dpi = 500,
	 type = "cairo")

figure_number <- figure_number + 1

```



```{r}

aux_df <- analysis_sample %>%
	select(pseudo_ResponseID,
		 contains("DataTrans"),
		 contains("ProcOrder")) %>%
	select(pseudo_ResponseID,
		 contains("importance"))
aux_df <- aux_df %>%
	pivot_longer(-pseudo_ResponseID,
			 names_to = "var_name",
			 values_to = "var_value")
aux_df <- aux_df %>%
	mutate(var_name = str_remove(var_name, "_importance"))
aux_df <- aux_df %>%
	mutate(var_name = factor(var_name,
					 levels = c("DataTrans",
					 	     "ProcOrder"),
					 labels = c("Data transformations",
					 	     "Processing order")))

aux_df <- aux_df %>%
	mutate(var_value = factor(var_value,
					  levels = c(NA,
					  	     "Not at all important",
					  	     "Slightly important",
					  	     "Moderately important",
					  	     "Very important",
					  	     "Extremely important"),
					  labels = c("n.a.",
					  	     "Not at all",
					  	     "Slightly",
					  	     "Moderately",
					  	     "Very",
					  	     "Extremely"),
					  exclude = NULL))

aux_df %>%
	ggplot(aes(x = var_value)) +
	geom_bar(color = "white", fill = "#56B4E9") + 
	theme_bw() +
	facet_wrap(vars(var_name)) +
	theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
	theme(strip.background = element_rect(fill = "white")) + 
	theme(strip.text = element_text(colour = "black")) + 
	labs(y = "Number of responses",
	     x = "") +
	My_Theme

ggsave(filename = here::here("figures",
				     paste0("Fig", figure_number,
				     	 "_importance_data_transformations.png")),
	 width = 10, height = 7, dpi = 500,
	 type = "cairo")

figure_number <- figure_number + 1

```


# Likelihood of reproducibility


```{r}

analysis_sample %>%
	filter(!is.na(likelihood_reproduce)) %>%
	arrange(likelihood_reproduce) %>%
	ggplot(aes(x = likelihood_reproduce)) +
	geom_bar(color = "white", fill = "#56B4E9") + 
	theme_bw() +
	theme(strip.background = element_rect(fill = "#56B4E9")) + 
	theme(strip.text = element_text(colour = "black")) + 
	labs(y = "Number of responses",
	     x = "Likelihood (0 to 100)") +
	scale_x_continuous(limits = c(0, 101)) +
	My_Theme

ggsave(filename = here::here("figures", 
				     paste0("Fig", figure_number, 
				     	 "_likelihood.png")),
	 width = 7, height = 4, dpi = 500,
	 type = "cairo")

figure_number <- figure_number + 1

mean(analysis_sample$likelihood_reproduce, na.rm = T)
sd(analysis_sample$likelihood_reproduce, na.rm = T)

```

# Software

```{r}

df_software <- analysis_sample %>%
	select(pseudo_ResponseID,
		 software_collect,
		 software_analyze)

# I will separate by comma, so I need to modify a few responses to make this easier
df_software <- df_software %>%
	pivot_longer(-pseudo_ResponseID,
			 names_to = "software_used_for",
			 values_to = "name_of_software")
df_software <- df_software %>%
	mutate(software_used_for = case_when(software_used_for == "software_collect" ~ "data_collection",
							 software_used_for == "software_analyze" ~ "data_analysis"))

df_software <- df_software %>%
	mutate(name_of_sw_edited = str_replace_all(name_of_software, pattern = "\\;", replacement = "\\,"))
df_software <- df_software %>%
	mutate(name_of_sw_edited = str_trim(name_of_sw_edited))

df_software <- df_software %>%
	mutate(name_of_sw_edited = 
		 	case_when(name_of_sw_edited == "Depends. Often I get from gov't sources." ~ "not_specified", 
		 		    name_of_sw_edited == "ePrime and Collector" ~ "eprime, collector",
		 		    name_of_sw_edited == "Gorilla Eprime others in the past we wrote the software ourselves" ~ "Gorilla, Eprime",
		 		    name_of_sw_edited == "jamovi, some recent work has been checked in both multi-level model and stimuli-as-fixed effects anova models in R by a highly trained person in MLM" ~ "jamovi, r",
		 		    name_of_sw_edited == "Mostly self developed software" ~ "not_specified", 
		 		    name_of_sw_edited == "PsychoPy (offline, my own Python code), JavaScript (for online studies, again my own code, no frameworks)" ~ "PsychoPy, JavaScript",
		 		    name_of_sw_edited == "recently testable, sometimes proprietary web coding, previously a lot of superlab studies, a long time ago custom programmed stuff (not by me)" ~ "testable, not_specified, superlab, custom code",
		 		    name_of_sw_edited == "Spss R Jamovi Excel sometimes" ~ "Spss, R, Jamovi, Excel",
		 		    name_of_sw_edited == "used lots, but mostly R (on the q below, depends what you mean open science). Ignore the response since the q is poor." ~ "R, not_specified",
		 		    TRUE ~ name_of_sw_edited))
df_software <- df_software %>%
	mutate(name_of_sw_edited = str_to_lower(name_of_sw_edited))

df_software <- df_software %>%
	mutate(copy_sw = name_of_sw_edited) %>%
	separate(col = copy_sw,
		   into = c("sw_1", "sw_2", "sw_3", "sw_4", "sw_5", "sw_6"),
		   sep = "\\,",
		   fill = "warn")

df_software <- df_software %>%
	pivot_longer(cols = starts_with("sw"),
			 names_to = "var_name",
			 values_to = "edited_software")

df_software <- df_software %>%
	filter(!is.na(edited_software))
df_software <- df_software %>%
	mutate(edited_software = str_trim(edited_software))
df_software <- df_software %>%
	filter(edited_software != "")

df_software <- df_software %>%
	mutate(edited_software = case_when(edited_software %in% c("custom code",
										    "custom made online") ~ "custom",
						     edited_software == "e-prime" ~ "eprime",
						     edited_software == "jspsch" ~ "jspsych",
						     edited_software == "lab.js" ~ "labjs",
						     edited_software == "matlab ptb" ~ "matlab",
						     edited_software == "matlab/octave" ~ "matlab",
						     edited_software == "open sesame" ~ "opensesame",
						     edited_software == "psychpy" ~ "psychopy",
						     edited_software == "pyschopy" ~ "psychopy",
						     edited_software == "spss (at the beginning)" ~ "spss",
						     TRUE ~ edited_software))

df_software <- df_software %>%
	mutate(edited_software = if_else(str_detect(edited_software, "presentation"), "presentation", edited_software))

df_software %>%
	filter(software_used_for %in% c("data_collection")) %>%
	group_by(software_used_for, edited_software) %>%
	summarise(n_obs = n(), 
		    percent = n()/nrow(df_software)) %>%
	arrange(desc(n_obs)) %>%
	print(n = 100)

df_software %>%
	filter(software_used_for %in% c("data_analysis")) %>%
	group_by(software_used_for, edited_software) %>%
	summarise(n_obs = n(),
		    percent = n()/nrow(df_software)) %>%
	arrange(desc(n_obs)) %>%
	print(n = 100)

aux_df <- df_software %>%
	filter(software_used_for == "data_analysis") %>%
	mutate(uses_R_for_analysis = if_else(edited_software == "r", 1, 0))

aux_df <- aux_df %>%
	group_by(pseudo_ResponseID) %>%
	summarise(uses_R_for_analysis = sum(uses_R_for_analysis)) %>%
	ungroup()

analysis_sample <- analysis_sample %>%
	left_join(aux_df,
		    by = c("pseudo_ResponseID"))

```


# Demographics

```{r}

analysis_sample %>%
	ggplot(aes(y = geographical_area)) +
	geom_bar(color = "white", fill = "#56B4E9") + #fill with blue color, white borders of the bars
	theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
	ylab("")

analysis_sample %>% 
	group_by(geographical_area) %>% 
	count() %>% 
	arrange(n) %>% 
	mutate(percent = n / nrow(analysis_sample))

analysis_sample <- analysis_sample %>%
	mutate(area_study = str_to_lower(area_study))



```


Number of times that specific terms were used to describe the area of study, by participants (n = `r nrow(analysis_sample)`) in the analysis sample: 

- "cognitive": n = `r nrow(analysis_sample %>% filter(str_detect(area_study, "cognitive")))`
- "psychology": n = `r nrow(analysis_sample %>% filter(str_detect(area_study, "psychology")))`
- "neuro": n = `r nrow(analysis_sample %>% filter(str_detect(area_study, "neuro")))`
- "linguistics": n = `r nrow(analysis_sample %>% filter(str_detect(area_study, "linguistics")))`


```{r}
sessionInfo()
```

